---
title: "Cabbages"
author: "Samira Quintero!"
date: "Fall 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
ggplot(veggy, aes(x = Cult, y = VitC)) +
geom_boxplot (fill = "lightblue", color = "black",outlier.color = "red", notch = TRUE) +
labs(
title = "Box Plot of VitC by Cult",
x = "Cult",
y = "Vitamin C"
)

```
C52 exhibits a higher level of vitamin C, according to the Boxplot.

A detailed inspection of the two boxes reveals that they are not connected, which indicates a significant discrepancy. 




<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results
```{r}
favstats(VitC~Cult,data=veggy)
```
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


Given their lesser size than the Q1 of C52, the Q3 of C39 appear to be truly discontinuous, according to the data.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
The p-value is .00000003405. This clearly shows C39 and C52 are very different from one another





# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->



I first told ChatGPT to build a box plot, then I told it to center the title and highlight outliers in red. I also asked Chat GPT to make further changes, including expanding the font.

When I was done, I requested ChatGPT to create a notch box plot.

When the date was examined, it was discovered that C52 has more vitamin C. This made it crystal clear that the two unconnected causes differed greatly from one another.
